### 2017-01-31 Radio/VLA_OH/VLA_proposal2017B.tex
remove future obs w/ A array part

% abstract:
% An exceptionally rare lensing configuration ?, providing a unique opportunity to explore the ISM conditions in this important but thus far unobservable(unexplored?unexploited?) regime of galaxy evolution. We propose to take advantage of the magnification of the lensed galaxy RXJ1131, a gas-rich merger with prodigious star formation rate of 120 \Msun yr\pmOne to search for OHM at intermediate-$z$, when the merger rate and ... . By combining this information with existing ?, we will ? These observations will ...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
\newcommand{\LOH}{$L_{\rm OH}$\xspace}
\newcommand{\rarr}{$\rightarrow$}
% \newcommand{\civ}{C{\scriptsize IV}}
% \newcommand{\heii}{He{\scriptsize II}}
\newcommand{\bco}{\mbox{CO(2-1)}\xspace}
\newcommand{\cco}{\mbox{CO(3-2)}\xspace}
\newcommand{\lohmax}{$L_{\rm OH}^{\rm max}$\xspace}
\newcommand{\lohpred}{$L_{\rm OH}^{\rm pred}$\xspace}
\newcommand{\lohlfir}{$L_{\rm OH}-L{\rm FIR}$\xspace}

@@

\begin{center}
{\large{\bf{Probing OH Megamaser in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{Current understanding of OH megamasers and galaxy evolution} \\
% point
% - OHM <-> ULIRGs <-> mergers <-> gas rich 
% - conditions for OHM
\indent Almost all ($>$95\%) OH ``megamasers" (OHMs) known to date are associated with 
(ultra)-luminous infrared galaxies (U)LIRGs (\LIR$>10^{11}$\,\Lsun; see \citealt[]{Lo05a} for a review), 
which are undergoing extreme bursts of star formation triggered by merger events
\citep[e.g.,][]{Sanders96a, Hopkins06b}.
Theoretically, the intense IR radiation field and the large column of molecular gas 
found in (U)LIRGs/mergers
are the required conditions for generating OHMs \citep[e.g.][]{Baan89a}.
%Since the necessary excitation of OHMs can be provided by 
%IR pumping (for pop. inversion) with large molecular column density \citep{Baan89a}, where 
%the required radiation is believed to be coming from dust absorbing starlight from 
%SB that are thought to be merger-driven (and AGN), and the high density at center easily reached in mergers.
Thus, starburst galaxies (IR-luminous) and mergers appear to be the most probable galaxy populations for hosting OHMs.

% point:
% - using OHM to trace distant merger
% - future survey using number density of OHM to constraint galaxy evolution models / merger history
% - currently no new detections beyond z>0.3, despite great efforts over the last two decades
% - our source is cheap to do, reasonable to expect OHM, we are probing deeper than previous attempts
The scaling relation of $L_{\rm OH}$$\propto L_{\rm FIR}^{2}$ 
\citep[or  $L_{\rm OH}$$\propto L_{\rm FIR}^{1.2}$ with Malmquist bias correction; \Fig{model}a; ][hereafter DG02]{Baan89a, Darling02b_LF} 
suggests that the number density of OHM is expected to increase towards $z$\ssim3,
when (U)LIRGs/mergers are more common \citep[e.g.,][]{LeFloch05a, Magnelli09a}.
OHMs have therefore been proposed as one of the most promising avenues for tracing mergers beyond the nearby universe
and for constraining the merger history of galaxies 
independent of IR luminosity function (\citealt{Briggs98a}, DG02). 
These models predict%  based on the commonly observed \LFIR$>$1\E{12}\Lsun at $z$\,$\gtrsim$\,1
that we should be able to detect OHMs out to at least $z$\ssim3 with current facilities 
(e.g. the GBT; \Fig{model}b). Yet, 
the most distant OHM host galaxy known-to-date is at $z$\eq0.265, which was 
discovered over two decades ago \citep{Baan92a}.
In addition, the null detections and unexpectedly low detection rate 
reported in the latest OHM studies (over half a decade ago) 
by \citet{Ivison06a} in a $z$\ssim4 galaxy % with an IR luminosity of \LIR$\gtrsim$1\E{14}\Lsun, 
and by \citet{Willett12a} in a sample of (U)LIRGs at $z$\,$\lesssim$\,1.5 (7\% detection rate, \Fig{model}) --- % only detected 9/121 
suggest a potential redshift evolution in the \LOH-\LFIR relation, which may hint at a different 
OHM triggering mechanism at earlier epochs that reflects the different physical conditions between
low- and high-$z$ (U)LIRGs.
The null detections in these studies also indicate also suggests that the 
classical model for OH pumping (pumped radiatively) in megamasers may not be universal (i.e., not all OHMs are unsaturated).
% only a radiative pumping mechanism for OH megamasers based on weak, unsaturated gain has been considered \citep{Henkel90a,Randell95a}.
%In these papers it was assumed that the maser cloud amplifies 
% radio emission from a source lying behind the cloud. 
However, since a purely radiative pumping mechanism is possible only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$). 
Theoretically, at relatively high OH densities, collisional processes may predominate. 
In addition, at high densities saturated amplification can be important \citep{Field94a}.
Detecting OHM beyond $z$\eq0.265 is therefore crucial to 
enable a better understanding of OHM and to 
improve existing predictions used for planning future OHM surveys with upcoming facilities 
\citep[e.g., FAST, APERTIF/WSRT, ASKAP;][]{Zhang14b}.
Here we propose to observe OH 1667 MHz line emission in the 
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\eq0.65 (\Fig{hst}) using the VLA's B-array configuration.

\noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\ 
\indent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is 
lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}). 
By exploiting the effect of lensing magnification, 
our proposed detection experiment requires {\bf an on-source time of  % sigma scales as 1/root(t) --> t scales as 1/sigma^2
$\sim$30 times less} than otherwise needed to reach the same sensitivity. 
The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}; e.g.,][]{Claeskens06a, Sluse07a, Pooley07a, Reis14a, Leung17a}, 
making it one of the best-studied galaxies at $z$$>$0.5 and 
the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}. 
The lensed nature of this target provides an excellent 
opportunity to study the innermost regions around a black hole at a cosmological distance.
In fact, X-ray studies constrained the X-ray emitting region a highly compact source of emission 
($\sim$20\,AU; constraining the optical and X-ray emitting region near the accretion disk down to pc-scale) \citep{Dai10a},
demonstrating the how much we already know about this target.
Features in the X-ray spectrum finds 
%  A fraction of this hard X-ray emission is reflected by cold gas in the accretion disk, producing an observed spectrum imprinted with the features of photoelectric absorption, fluorescent 6.4 keV Fe K$\alpha$ line emission, and a Compton backscattered reflection continuum that produces a bump in the spectrum above 10 keV (George & Fabian 1991).
 % The continuum is strongly absorbed at soft energies by a 
a neutral gas of column density $N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ near the accretion disk. % w.in the X-ray emitting region
The spectrum at lower energies is heavily absorbed by neutral gas with a hydrogen column density $N_{\rm H}$.
% Soft X-ray continuum suggest the presence of a substantial amount of gas.
Our best-fit spectral energy distribution (SED) model indicates
a strong apparent far-IR luminosity of \LFIR$>$4\E{12}\,\Lsun, which corresponds to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected).
These properties together with the evidence of recent star formation (as traced by rest-frame UV \obs),
the presence of a nearby companion at $\sim$2.4\,kpc away, and a large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}) 
are favourable for generating OHMs, suggesting RXJ1131 is an ideal candidate 
to search for OHM beyond the nearby universe.

In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of 
$\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region 
free of RFI at the low-end of the L-band. 
This together with the high fringe rate of the B-array configuration will 
reach a sensitivity deeper than previous high-$z$ OHM searches beyond $z$$>$0.4, which were carried out 
with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.

%--- added
% what can OHM help us understand the physical conditions of high-z galaxies. 
% what can't we learn from local OHM but can at high-z.
% difference between local and high-z; why care about doing OHM at high-z
The number density of IR-luminous galaxies and their molecular gas fractions and SFRs
are higher towards $z$\ssim2,
indicating a different physical conditions between low- and high-$z$ galaxies.
Such a different physical conditions can potentially be reflected in the OHM phenomenon, given that OHM are more strongly amplified in 
large column of molecular gas and the more intense IR radiation field.
Given that OHMs originate from central region, detecting OHM in high-$z$ galaxies and comparing them against those in the local, which are 
relatively more quiescent, would allow us to directly probe the physical conditions (and dynamics) in the inner few hundred pc
as galaxies evolve. {\bf justify the masing, pumping mechanism in science goals}
% foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
In fact, the null detection of OHM in a $z$\ssim4 galaxy with \LIR$>$1\E{13}\,\Lsun already hints at a different 
excitation mechanism that may be a result of their different physical conditions (e.g. more dense, higher optical depth \citet{Ivision06a}).

% X-ray and LOH -- why RXJ1131
Because OHMs are associated with the most luminous galaxy in the nearby universe, it is reasonable to speculate a possible connection
between OHMs and quasars, where both are driven by mergers (increasing \LFIR, and molecular gas into central region) 
since recent high-$z$ studies find evidence that AGN activity and mergers are connected (growth of SMBHs may be partly driven by 
mergers) \citep{DiMatteo05a}.
pumping and density, saturated:
 A purely radiative pumping mechanism is possible only at relatively low densities
($n_{\rm OH}$\ssim10$^{-4}$ cm$^{-3}$). At relatively high OH densities, collisional processes may predominate. In addition, at high densities
saturated amplification can be important.
While in the nearby universe (z\ssim0), OHMs appear to be unsaturated. But this may not be the case at high-$z$, where
 the physical environment is very different, more violent star formation, the ISM is more turbulent, and when there are more gas 
 available on average.
Further \obs of OHM are needed to elucidate the role of collisional processes in 
producing population inversions over the observed radiative transitions of OH.
% while locally, not all OHM are AGN hosts, suggesting the FIR radiation from the SB is the dominant pumping source, but the non-detection based on local extrapolation and such maser model may suggest a different energy source/powering mechanism/ at higher-z, where quasars are more active, and may indicate that something about AGN/radio pumping? saturated amplification?

%-------

\noindent \textbf{Science goals} \\

\indent The proposed \obs will establish the first measurement of an OHM in a {\it bona-fide} high-$z$ merger, thereby
demonstrating the feasibility of using it as a tracer of distant galaxy mergers and
testing the long-envisaged hypothesis of using the number density of OHM to constrain 
the redshift evolution of merger rate. 
Such a
high-$z$ (non-)detection will also allow us to better constrain the \LOH-\LFIR scaling relation and its redshift evolution,
and thus improve 
% current models used to predict OHM detection rate 
predictions on the detection threshold needed  
% model predictions for designing 
% when designing
% future surveys to search for 
to carry out systematic searches of high-$z$ OHMs with upcoming facilities.  
% because if we find a shallower relation, then it would mean the surveys need to go deeper to reach the same \LOH.
Since our target is a merger, 
a null detection would also indicate that the notion of 
using the OHM number density to constrain the merger history needs to be revised before designing future OHM surveys.

% --  host properties ---
% to further understand the relationship between OHM and the types of galaxies hosting them at an earlier epoch.
In addition, regardless of whether the OH line emission is detected or not, the amount of data we have already acquired 
for this potential OHM host galaxy will allow us to compare its (host) galaxy properties 
(e.g., SFR or \LFIR, \LIR, \LOH, $L_{\rm radio}$, molecular and dust content)
against those of local OHM hosts to better understand 
% the nature of OHM.
% the pumping and masing mechanism of OHM. % the condition needed for generating OHM
% the required conditions for triggering OHM at an earlier epoch.
the relationship between the maser emission and the environment of its (host) galaxy. 
{\bf  Is there some
detailed prediction that they should be found in things above a
certain SFR or merger state or something? Any more details you can
provide there would be better. But 2-3 sentences about this would be good.
LFIR, LRadio.. LOH.. 
}
% --- to better understanding the pumping and masing mechanism --
To blah... saturated maser and collisional pumping. % saturated gain mechanism
% The T/density of the masing material? 
% Maybe you could do some of that with
% certain reasonable assumptions? Similarly 2-3 sentences would be good.
% 
Because of the required condition to excite and generate OHM, and because they originate from the central few pc to few hundred pc 
in the nuclear regions of galaxies \citep{Diamond99a},
OHM is a powerful diagnostics of the physical 
conditions in the innermost regions of galaxies. 
% foreground amplification of background radio continuum, this quadratic relationship may be expected, if the population inversion is pumped by the FIR radiation field and the radio continuum (which itself is proportional to the FIR luminosity) is being amplified by an unsaturated maser cloud
Classical model of OHMs suggest that low-gain amplification (i.e., unsaturated gain) and IR pumping 
is the dominant mechanism for producing OHM. However, the null detections of OHM at $z$$>$0.3
\citep{Ivison06a, Willet12a} may suggest different pumping efficiency (\LOH/\LFIR) at high-z, due to the different physical conditions (e.g. 
optical depth is higher at high-z due to the higher LFIR). 
% 
% Since FIR radiation field can invert the OH population via the ``pumping lines'' at 35 and 53$\mu$m
% Masing can then be stimulated by 18 cm (i.e. $\sim$1.6GHz).
% With the additional constraint on the \LOH-\LFIR relation at $z$$>$0.3 provided by this experiment, we will 
% investigate the pumping efficiency at higher redshift than currently studies, %% but presumable can already do so with upper limits from Willett+12
% by comparing to local OHM hosts and as a function of \LFIR through the \LOH-\LFIR scaling relation. % (look for potential discrepancy in this relation based on nearby studies)% (already seen a discrepancy at z=3, see also Darling02b find evidence of a mixture of saturated and
% unsaturated masers). 
% For instance, a slope shallower than $<$2 %  (i.e, deviations from the quadrature) 
% would suggest that the amplification process is less efficient at higher FIR luminosity. %, where the optical depth is higher.
% Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
% (i.e., unsaturated masing) found to be consistent with local OHMs
% will likely break down resulting in deviations from the quadratic relation 
% implying the simple picture of low-gain amplification (i.e., unsaturated masing) 
% found to be consistent with local OHMs will likely break down
% and indicate saturated masing at high redshift.
% Darling02b: find evidence of a mixture of saturated and unsaturated masers. 
% 
A non-detection would therefore still be meaningful in advancing our knowledge.

% --- procedure
%Existing lens modeling of RXJ1131 have been carried out from rest-frame X-ray through submm, indicating BLAH component is strongly-lensed by a factor of $\mu$\ssim10. 
%Since the OHM is expected to originate from the few hundred pc from the central quasar \citep[e.g.][]{Darling07a}, thus 
%we will correct for lensing using the magnification factor based on X-ray, MIR lens model \citep{}.

With the aid of lensing and the rich multi-wavelength data 
% probing a wide range of properties 
available for this potential OHM host, RXJ1131 is an exceptional target
for obtaining a better understanding of OHM in IR-luminous galaxies beyond the nearby universe out to
a lookback time of $\sim$6 Gyr.
% The detection of a OHM at redshift higher than already known 
% may also open up/demonstrate the possibility of use OHM as a tool for studying the 
% properties (dynamics) of the molecular nuclei at high redshifts when observed at high resolution with the VLBI.
In the case of a detection, we will future carry out follow-up \obs % at higher-resolution 
with the VLBI to study the physical conditions of the nuclear molecular torus
% and to better understand the energy source and the nature of OHM at high redshift.
% ($<$ few hundred pc) 
responsible for the OH line emission, where the velocity structure of the 
currently highest-$z$ OHM already suggests a different dynamic structure 
than those at lower-$z$ \citep{Baan92a}. % . e..g IRAS F14070+0525 has a total line width of ~2400 km/s 
% OHM may be useful for studying dynamical and molecular properties of nuclei at high-z. <-- well, but APM is not detected.. so OHM may not be so reliable.
The proposed investigation will therefore serve as an
important benchmark for future studies of high-$z$ OHM out to earlier epochs,
when extremely IR-luminous sources are much more common.
%  inform future systematic searches of high-$z$ OHMs 
% Thus, a detection/non-detection at this redshift is crucial for development of this technique for future OHM studies.

%\noindent \textbf{Technical Justification}
%We estimate the required sensitivity based on the \LFIR of 4\E{12}\,\Lsun found for RXJ1131 
%together with the \LOH$\propto$\LFIR$^{1.2}$ relation reported by (DG02), and 
%the typical FWHM line width of $\sim$600\,\kms of the highest-$z$ sources ($z$$>$0.2; DG02).
%These yield a line intensity of 330 mJy\,\kms, and a peak flux density of $S_\nu$\eq0.55\,mJy.
%To secure a 5$\sigma$ detection, we therefore require $\sigma$\eq0.11\,mJy beam\pmOne over the line FWHM. 
%Since extragalactic OHMs originate from the central few hundred pc, we expect the emission to 
%remain spatially-unresolved at the B-array configuration.
%We thus require an on-source time of 4.3 hours (total time of 5.5 hours).
%% \vspace{-0.25em}

%% ------------------------------------------------------------
%% REFERENCES
%% ------------------------------------------------------------
\noindent \textbf{References}
{\fontsize{10pt}{12pt}\selectfont
    \bibliography{master_cleanup}
}
% \vspace{-1.25em}

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Lsun}{\mbox{$L_{\odot}$}\xspace}
\newcommand{\Msun}{\mbox{$M_{\odot}$}\xspace}
\newcommand{\LIR}{\mbox{$L_{\rm IR}$}\xspace}
\newcommand{\LFIR}{\mbox{$L_{\rm FIR}$}\xspace}
\newcommand{\LOH}{$L_{\rm OH}$\xspace}
\newcommand{\rarr}{$\rightarrow$}
% \newcommand{\civ}{C{\scriptsize IV}}
% \newcommand{\heii}{He{\scriptsize II}}
\newcommand{\bco}{\mbox{CO(2-1)}\xspace}
\newcommand{\cco}{\mbox{CO(3-2)}\xspace}
\newcommand{\lohmax}{$L_{\rm OH}^{\rm max}$\xspace}
\newcommand{\lohpred}{$L_{\rm OH}^{\rm pred}$\xspace}
\newcommand{\lohlfir}{$L_{\rm OH}$-$L_{\rm FIR}$\xspace}

@@

\begin{center}
{\large{\bf{OH Megamaser Emission in a Strongly-Lensed Gas-Rich Merger at $z$\ssim0.65}}}
\end{center}
\vspace{-.8em}
\textbf{OH megamasers and the physical conditions of low- and high-$z$ \galpop}
Galaxies with high IR luminousity and thus intense star formation rate are important for the build-up of stellar mass in the universe. 
While IR-luminous galaxies ($\gtrsim10^{12}$\Lsun; ULIRGs) 
exist at both low and high redshifts ($z$), recent studies indicate that they are not the same population. 
Low-$z$ ULIRGs are mostly merger-triggered starbursts which are more compact and contain
less molecular gas compared to their \highz counterparts \citep{Veilleux02a, Hopkins10a, Rujopakarn11a, Rujopakarn13a},
whereas \highz starbursts are driven by cold gas accretion \citep[e.g.,][]{Dekel09b} 
and/or galaxy mergers \citep{Riechers11a, Riechers13b, Hayward12a}.
Probing the kinematics, dynamical structures, and physical conditions of the inner regions of \highz ULIRGs, 
and comparing them to those observed at low $z$ 
are necessary to better understand the internal structures of starbursting galaxies at different epochs.
% a comparison with their local analogs are important to enable a better understanding of the nature of these \galpop and
% to shed light on their formation and evolution processes.
% improve our understanding of the formation and evolution of low- and \highz starburts.
However, measuring these properties at high $z$ (e.g., $\sim$8\,kpc/$''$ at $z$=1)
% measuring the kinematics in the inner regions of high-$z$ galaxies 
require sub-arcsec resolution or better with typical line tracers. On the other hand, a 
steep relation ($L_{\rm OH}\propto L_{\rm FIR}^{1.2-2}$; \Fig{model}a) has been found in nearby OH ``megamasers'' 
(OHMs), which are generated in the inner few hundred pc of U/LIRGs (see \citealt[]{Lo05a} for a review).
Given the ubiquity of IR-bright galaxies at high-$z$, we propose that OHM may be used as a tracer to 
study the kinematics and dynamics of the inner regions of \highz galaxies.
In fact, the much broader linewidths found in $z$$>$0.2 OHMs compared to those at $z$=0 already hint at the feasibility of 
this diagnostic \citep[hereafter DG02]{Baan92a, Darling02a}.

\noindent Existing models predict that detections of
OHMs out to at least $z$\ssim3 are possible with current facilities (e.g., the GBT; \Fig{model}b; \citealt{Darling02b_LF}).
Yet, despite several attempts,
the most distant OHM known-to-date was discovered over two decades ago, at $z$\eq0.265 \citep{Baan92a}.
The null detection in a $z$\ssim4 extremely IR-bright galaxy (\LIR$>10^{14}$\Lsun; \citealt{Ivison06a}) and
the remarkably low detection rate (7\%) from a sample of $>$120 IR-luminous galaxies
at $z$\,$\lesssim$\,1.5 ($L_{\rm IR}>10^{11}$\Lsun; \Fig{model}b; \citealt{Willett12a})
suggest a potential redshift evolution in the \LOH-\LFIR relation.
Detecting OHM beyond $z$\eq0.265 is therefore necessary to enable a better understanding of the
OHM trigger mechanism, which may differ at earlier epochs due to different physical conditions of galaxies;
to demonstrate the utility of using it as a tracer of the kinematics in the inner regions of high-$z$ galaxies (with upcoming facilities,
e.g., FAST, APERTIF/WSRT, ASKAP; \citealt[][]{Zhang14b});
and to improve existing predictions for future OHM surveys with these facilities.
Here we propose to observe OH 1667 MHz line emission in the
gravitationally-lensed starbursting galaxy merger
RXJ1131 at $z$\ssim0.65 (\Fig{hst}) using the VLA's B-array configuration.

\noindent \textbf{An ideal target --- a lensed gas-rich, starbursting merger at $z$\,$>$\,0.6}\\
\noindent High-resolution imaging and spectroscopy in optical wavelength show that RXJ1131 is
lensed by a foreground galaxy at $z$\ssim0.3 (\Fig{hst}; \citealt{Sluse03a}).
The unique lensing configuration of RXJ1131 has led to extensive follow-up studies spanning X-ray to radio \citep[\Fig{hst}e; e.g.,][]{Claeskens06a, Sluse07a, Leung17a},
making it one of the best-studied galaxies at $z$$>$0.5 and
the only source at 0.2$<$$z$$<$1 with spatially-resolved imaging of the molecular gas distribution \citep{Leung17a}.
Modeling of the X-ray spectrum reveals substantial amount of neutral gas with column density of
$N_{\rm H}\sim$10$^{23}$ cm$^{-2}$ in the innermost region near 
the $L_X$$\gtrsim$10$^{45}$\,\Lsun AGN \citep{Pooley07a, Reis14a}.
Our best-fit spectral energy distribution (SED) model indicates
a strong apparent far-IR luminosity of \LFIR$\sim$5\E{12}\Lsun, corresponding to
an intense star formation rate of SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a cold dust temperature of $T_{d}$\eq55K
(i.e., based on FIR/submm photometry).
The large column density together with the strong FIR radiation field
% of $\sim$10$^{12}$\Lsun (lensing-corrected),
% recent star formation (as traced by rest-frame UV emission),
and the large molecular gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun (\Fig{hst}b, c)
are favourable for generating OH masers, making RXJ1131 an ideal candidate
to search for OHMs beyond the nearby universe.

\noindent In addition, the redshift of RXJ1131 has been spectroscopically confirmed with CO lines down to a precision of
$\Delta z$\eq0.0002, indicating that the proposed OH line is redshifted to a fortuitous region
free of RFI at the low-end of the L-band.
Together with the high fringe rate of the B-array configuration, the proposed \obs will
probe deeper than previous OHM searches beyond $z$$\gtrsim$0.3, which were carried out
with single-dish telescopes \citep[\Fig{model}b; e.g.][]{Darling02a, Willett12a}.
Assuming the Malmquist-bias corrected relation
($L_{\rm OH}\propto L_{\rm FIR}^{1.2}$; DG02), 
we expect an apparent OH luminosity of \LOH= 3.3\E{3}\,\Lsun (orange marker in \Fig{model}).
Since Mrk 231 --- an OHM host with both an AGN and starburst, and thus the most similar to RXJ1131 ---
falls above this relation, our assumption and the required sensitivity are reasonable for our target.
We here aim at a 7$\sigma$ detection.
By exploiting the effect of lensing magnification, we require an {\bf on-source time of 8.0 hours}, which
is {\bf $\gtrsim$30 times cheaper}
 % sigma scales as 1/root(t) --> t scales as 1/sigma^2
than otherwise possible.

\noindent \underline{\textbf{Science goals}}
\vspace{.2em}\\
\noindent $\bullet$ {\bf Physical conditions and OH pumping mechanisms in low- and high-$z$ galaxies.}
Null detections in previous high-$z$ OHM searches suggest a shallower \LOH-\LFIR dependence, which may be
reflecting the different physical conditions of the inner few hundred pc (where OHMs are generated)
between low- and high-$z$ IR-luminous galaxies.
The lower \LOH/\LFIR indicate that the OH amplification is less efficient at the same FIR luminosity
and that collisional pumping (e.g., due to higher gas mass and density, and 
AGN heating; \citealt{Field94a}) % volume density
%
% Since a purely radiative pumping mechanism is possible
% only at relatively low densities ($n_{\rm OH}$\ssim10$^{-4}$\,cm$^{-3}$), and collisional processes can theoretically predominate at high OH densities, and saturated amplification can become important \citep{Field94a}.
may play a dominant role in these \highz gas-rich systems.
Obtaining a definitive OHM measurement in RXJ1131 will provide a handle on the OH pumping efficiency (\LOH/\LFIR) out to higher $z$.
This together with the detailed properties derived for our target (e.g., \LFIR, \LIR, SFR, $L_{\rm radio}$, $T_{d}$, molecular and dust content)
will elucidate the role of collisional over radiative pumping
that may be prevalent in \highz galaxies, given that their physical properties are more similar to RXJ1131 than
local starbursts. % more violent star formation in a more gas-rich turbulent ISM.
%	% [NOT applicable] Since the optical depth increases with FIR radiation field, the simple picture of low-gain amplification
%	% (i.e., unsaturated masing) found to be consistent with local OHMs...
%	%
%% % implying the simple picture of low-gain amplification (i.e., unsaturated masing, quadrature, low density)  \citep{Henkel90a,Randell95a} found to be consistent with local OHMs will likely break down; (i.e., not all OHMs are unsaturated).
%% While in the nearby universe (z\ssim0), OHMs appear to be unsaturated.

\noindent $\bullet$ {\bf OHM as a tracer of the kinematics in the innermost region of distant galaxies.}
The much broader linewidths found in $z$$>$0.2 OHMs \citep[typically at least a factor of $>$2 in FWHM;][DG02]{Baan92a}
compared to those at $z$\eq0 already indicate
different dynamical properties in the innermost regions of low- and high-$z$ OHM hosts.
Detecting the OHM in RXJ1131 will therefore demonstrate the feasibility of
using it as a tracer of the circumnuclear kinematics of \highz galaxies, which contain higher 
gas fractions and are much more turbulent than local galaxies, thereby improving
our understanding of the internal dynamics of violently star-forming galaxies at high $z$.

\noindent $\bullet$ {\bf Testing OHM as a tracer of mergers.}
The proposed \obs will establish the first OHM measurement in a {\it bona-fide} high-$z$ merger, thereby
demonstrating the feasibility of using it as a tracer of distant mergers and
testing the long-envisaged hypothesis of using its number density to constrain
the redshift evolution of merger rate (DG02).
Such a detection will also allow us to better constrain the
\LOH-\LFIR relation out to higher $z$, % which may provide a handle on the pumping efficiency (\LOH/\LFIR)
% that may be closer to other high-$z$ galaxies if their physical conditions are more similar than compared to low-z (\LOH/\LFIR)
and thus improve predictions on the required sensitivity needed for future searches of high-$z$ OHMs.
Since our target is a merger,
a null detection would also indicate that the notion of
using the OHM number density to constrain the merger history requires revision before designing future OHM surveys.

\noindent $\bullet$ {\bf Radio continuum.}
The proposed \obs will also provide an additional constraint on the radio continuum emission at 1\,GHz 
towards RXJ1131, and thus to constrain the radio spectral index (\Fig{hst}e).

% --- finally ----
\noindent
With the aid of lensing and the rich multi-wavelength data available for this potential OHM host, RXJ1131 is an exceptional target
for high-$z$ OHM search. 
Detecting the OHM will provide a handle on the pumping efficiency (\LOH/\LFIR)
and enable a better understanding of the OHM triggering mechanism at $z$\ssim0.65, which
would reflect the different physical conditions between low- and high-$z$ IR-luminous galaxies.
The detection will also demonstrate the utility of OHMs as tracers of distant mergers, and
of the kinematics in the inner few hundred pc
of starburst galaxies beyond the nearby universe. %, out to a lookback time of $\sim$6 Gyr.
The proposed investigation will therefore serve as an
important benchmark for future studies of high-$z$ OHMs out to earlier epochs,
when extremely IR-luminous starbursting sources are much more common.

%% ------------------------------------------------------------
%% REFERENCES
%% ------------------------------------------------------------
\noindent \textbf{References}
{\fontsize{10pt}{12pt}\selectfont
    \bibliography{master_cleanup}
}
\vspace{-0.9em}

\begin{figure}[ptbh]
\includegraphics[trim=0 0 0 0, clip, scale=0.8]{Fig/OHFIR_RXJ} % \hspace{-1.25em}
\includegraphics[trim=0 -20 155 0, clip, scale=0.39]{Fig/willett12_fig1_mod.pdf}
\vspace{-0.5em}
\caption{{\bf \LOH-\LFIR correlation and existing OHMs measurements}
{\it (a):} Since the OH line strength increases with \LFIR,
the ubiquity of IR-luminous galaxies at high $z$ suggest that OHM may be a used as a proxy for
studying the kinematics of the inner regions of distant galaxies.
(Figure modified from DG02).
{\it (b):} The highest-$z$ OHM known ($z$\eq0.265) was discovered over two decades ago.
Subsequent surveys (black and green symbols) suggest a potential redshift evolution in the \LOH/\LFIR relation
due to the different physical properties between low- and high-$z$ IR-luminous galaxies, but 
severe RFI contaminations at $\nu_{\rm obs}$$<$1\,GHz inhibit a definitive conclusion. (Figure adopted from
\citealt{Willett12a}).
Here we propose to observe OH 1667 MHz line emission in the gravitationally-lensed starbursting
galaxy merger RXJ1131 at $z$\eq0.65.
Assuming $L_{\rm OH}\propto L_{\rm FIR}^{1.2}$ (Malmquist-bias corrected; DG02),
we expect an apparent \LOH= 3.3\E{3}\,\Lsun in our target (orange marker). The proposed sensitivity will
probe deeper than existing OHM surveys (we do not expect RFI at the 
redshifted line frequency), 
and to fainter intrinsic (i.e., lensing-corrected) \LOH beyond $z$$\gtrsim$0.3.
Detecting the OHM in RXJ1131 will provide the first measurement beyond $z$$>$0.265,
which will improve predictions on the sensitivity needed for future high-$z$ OHM surveys with upcoming facilities.
\label{fig:model}}
\end{figure}

\begin{figure}[ptbh]
% \hspace{-1.6em}
\centering
\includegraphics[trim=0 190 0 0, clip, scale=.77]{Fig/Fig2}
\vspace{-0.85em}
\caption{
{\bf Our target RXJ1131, a gas-rich, starbursting merger at $z$\ssim0.65}
{\em (a):} Source-plane reconstruction of {\it HST} images shows recent star formation in our target and
the presence of a nearby companion (\citealt{Claeskens06a}).
{\em (b):}
The UV starlight in RXJ1131 is lensed into an Einstein ring (diameter $\sim$3.6") and the central AGN is
quadruply-lensed in the {\it HST} image (grayscale). Both star formation and the AGN are sustained
by the extended CO gas reservoir \citep[contours; ][]{Leung17a}.
{\em (c):}
Lens modeling of our CO data (yellow) 
reveals a massive gas reservoir of $M_{\rm gas}$\,$\gtrsim$\,10$^{10}$\Msun in RXJ1131 
(cyan; magnification factors $\mu_{L}$ are annotated above the respective channels) and
confirmed the presence of a CO-emitting companion, with a gas mass ratio of 7:1 \citep[bottom panel;][]{Leung17a}.
{\em (d):}
We have detected strong radio continuum emission at 5\,GHz towards this target.
The proposed \obs will provide an additional constraint at 1\,GHz (orange marker in \Fig{hst}e).
{\em (e):} Our best-fit SED model indicates a strong apparent far-IR radiation of \LFIR$>$4\E{12}\,\Lsun, corresponding to
an intense SFR\ssim120 \Msun yr\pmOne (lensing-corrected), and a dust temperature of $T_{d}$\eq55 K.
The massive gas reservoir, on-going star formation with high \LFIR and $T_{d}$, and the large gas column density
are favourable for generating OHM, making RXJ1131 an
ideal candidate to search for OHM beyond the nearby universe.
Here we aim to detect the OHM in RXJ1131, and thus to obtain a handle on the pumping efficiency
to better understand the triggering mechanism at a look-back time of 6 Gyr, which
would reflect the different physical conditions of the innermost regions between low- and high-$z$ IR-luminous galaxies.
The proposed study is therefore an important step towards understanding 
% the evolution of the inner few hundred pc of
the internal structure and kinematics of
starbursting galaxies at earlier epochs.
\label{fig:hst}}
\end{figure}
